Towards a Practical Face Recognition System: \\ Robust Alignment and Illumination by Sparse Representation

### 2011-04-04 faces_system.tex
Added my biography, switched to subfig

\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amscd}
\usepackage{amssymb}
\usepackage{subfigure}
\usepackage{pdfsync}
\usepackage{helvet}
\usepackage{url}
\usepackage{color}

@@

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{bios/arvind}}]{Andrew Wagner}
Arvind Ganesh received his Bachelor's and Master's degrees, both in Electrical
Engineering, from the Indian Institute of Technology, Madras, India in 2006. He
is currently a PhD candidate in the Electrical \& Computer Engineering
Department at the University of Illinois, Urbana-Champaign. His research
interests include compressed sensing, computer vision, and machine learning.
His recent work focuses on low-rank matrix recovery techniques for
batch image alignment and texture rectification.  \end{IEEEbiography}

@@

% or if you just want to reserve a space for a photo:

%
%\begin{biography}{Andrew Wagner}
%Biography text here.
%\end{biography}
%
%\begin{biography}{John Wright}
%Biography text here.
%\end{biography}
%
%\begin{biography}{Arvind Ganesh}
%Biography text here.
%\end{biography}
%
%\begin{biography}{Zihan Zhou}
%Biography text here.
%\end{biography}
%
%\begin{biography}{Yi Ma}
%Biography text here.
%\end{biography}
%

@@

% that's all folks
\end{document}

>>>>

\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amscd}
\usepackage{amssymb}

%\usepackage{subfigure}

%\ifCLASSOPTIONcompsoc
 %\usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
%\else
 %\usepackage[caption=false,font=footnotesize]{subfig}
%\fi
\usepackage[caption=false,font=footnotesize]{subfig}

\usepackage{pdfsync}
\usepackage{helvet}
\usepackage{url}
\usepackage{color}

@@

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{bios/arvind}}]{Andrew Wagner}
Andrew Wagner received his Bachelor's degree in General Engineering,
and his Master's degree in Electrical Engineering, from the University
of Illinois at Urbana-Champaign, where he is currently a Ph.D. 
candidate in Electrical \& Computer Engineering.
His research interests include robotics, computer vision, and optimal control.
His recent work focuses on parallel algorithms for sparsity
based face recognition.\end{IEEEbiography}

@@

@@

\end{document}
